Astropy - New software standards for a growing community

### 2017-09-20 main.tex
Update on Overleaf.
cite

The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community. Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3. In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in Astropy Collaboration et al. (2013).
(ordered in the order in which they appear in the astropy documentation)

>>>>

The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community. Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3. In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{2013A&A...558A..33A}.
(ordered in the order in which they appear in the astropy documentation)
